% Created 2019-04-18 jeu. 16:41
% Intended LaTeX compiler: pdflatex
\documentclass[11pt, a4paper]{./style}
                  \usepackage{natbib}
                  \usepackage{comment, csquotes}
                  \usepackage[adobe-utopia]{mathdesign}
                  \let\progstruct=\texttt
                  \newcommand{\progexample}[1]{{\ttfamily\small #1}}

\usepackage{amsmath}
\usepackage{amstext}
\usepackage{paralist}
\usepackage[utf8]{inputenc}
\usepackage[official]{eurosym}
\usepackage{booktabs}
\usepackage{ragged2e}
\usepackage{graphicx}
\usepackage{microtype}
\author{jsay@inra.fr}
\date{\today}
\title{Jean-Sauveur Ay}
\begin{document}

\maketitle


\titre{Contact Information}
\label{sec:org407d080}

\begin{center}
\begin{tabular}{ll}
\textbf{Phone:} & 00.33.(0)3.80.77.23.19\\
\textbf{Email:} & \href{mailto:jsay@inra.fr}{jsay-at-inra-dot-fr}\\
\textbf{Address:} & \href{http://www.inra.fr/en/Scientists-Students}{Inra}, \href{http://www.dijon.inra.fr/cesaer/en/axis/}{UMR Cesaer}\\
 & \href{https://www.google.com/maps/?q\%3D47.3097819,5.0644835}{26 blvd Dr Petitjean}\\
 & \href{https://www.google.com/maps/place/21000+Dijon/}{21000 Dijon (France)}\\
\textbf{Web pages:} & \href{https://www.dijon.inra.fr/cesaer/membres/jean-sauveur-ay/}{Cesaer} / \href{http://github.com/jsay/}{GitHub} / \href{https://ideas.repec.org/e/pay77.html}{RePEc} / \href{https://www.researchgate.net/profile/Jean\_Sauveur\_Ay}{ResearchGate} / \href{https://scholar.google.fr/citations?user=arEwxlIAAAAJ\&hl=fr}{Scholar}\\
\end{tabular}
\end{center}

\titre{Professional experience}
\label{sec:org4887acc}

\begin{center}
\begin{tabular}{ll}
2014 to now & \textbf{Researcher} at INRA, \href{http://www.dijon.inra.fr/cesaer/en/axis/}{UMR Cesaer} Dijon\\
2013 to 2014 & \textbf{Research fellow} at INRA, \href{https://www.versailles-grignon.inra.fr/economie\_publique\_eng/}{UMR Éco Pub} Paris\\
2011 to 2013 & \textbf{Postdoctoral fellow} at CNRS, \href{http://cesco.mnhn.fr/en}{UMR Cesco} Paris\\
\end{tabular}
\end{center}

\titre{Education}
\label{sec:orgdbe3a99}

\begin{center}
\begin{tabular}{ll}
2008 to 2011 & \textbf{PhD in Economics} at INRA and \href{http://en.u-bourgogne.fr/}{Université de Bourgogne}\\
2007 to 2008 & \textbf{MA in Economics} at \href{https://www.parisschoolofeconomics.eu/en/}{PSE, Paris School of Economics}\\
2005 to 2007 & \textbf{MA in Economics} at \href{https://www.amse-aixmarseille.fr/en}{Université Aix-Marseille II}\\
\end{tabular}
\end{center}

\titre{Fields of interest}
\label{sec:orgc02e3e0}

\begin{description}
\item[{Land Economics}] Land use choices and land price patterns in
relation to agricultural, environmental and
urban outcomes. Impacts of public policies
related to land use and land prices.
\item[{Wine Economics}] Consumers' preferences for wine characteristics,
vineyard prices in relation to geographical
indications and environmental factors. Impacts
of public policies related to the wine sector.
\item[{Applied Econometrics}] Spatial econometrics, geographically
weighted regression, treatment effects, best unbiased
predictions, discrete choice models.
\end{description}

\titre{Publications}
\label{sec:org2c0fc93}
\soustitre{Refereed papers (in English)}
\label{sec:org8e4f6a3}

\begin{itemize}
\item \textbf{Bioeconomic impacts of agroforestry policies in France} (with
Lauriane Mouysset, Claire Rais Assa, Frédéric Jiguet, Romain
Lorrilière, Luc Doyen). \emph{Land Use Policy}, 2019, 85, 239--248.  [
\href{bib/BIOFOR.bib}{bib} ; \href{https://www.sciencedirect.com/science/article/abs/pii/S0264837718308160}{link} ]
\item \textbf{Does issuing building permits reduce the cost of land? An
estimation based on the demand for building land in France} (with
Jean Cavailhès, Mohamed Hilal and Julie Le Gallo). \emph{Economics and
Statistics}, 2018, 500-501-502, 45--67.  [ \href{bib/PCPX.bib}{bib} ; \href{doc/PCPX-FILE.pdf}{file} ; \href{doc/PCPX-SUP.pdf}{sup} ;
\href{https://insee.fr/en/statistiques/3621981?sommaire=3622133}{link} ]
\item \textbf{Nonlinear impact estimation in spatial autoregressive models}
(with Kassoum Ayouba and Julie Le Gallo). \emph{Economics Letters},
2018, 163: 59--64. [ \href{bib/NLSP.bib}{bib} ; \href{doc/NLSP-FILE.pdf}{file} ; \href{doc/NLSP-SUP.pdf}{sup} ; \href{https://www.sciencedirect.com/science/article/pii/S0165176517304846}{link} ]
\item \textbf{Distance decay in the willingness to pay for wine: Disentangling
local and organic attributes} (with Raja Chakir, and Stéphan
Marette). \emph{Environmental and Resource Economics}, 2017, 68(4):
997--1019. [~\href{bib/DWTP.bib}{bib} ; \href{doc/DWTP-FILE.pdf}{file} ; \href{doc/DWTP-PRES.pdf}{pres} ; \href{doc/DWTP-SUP.pdf}{sup} ; \href{https://link.springer.com/article/10.1007/s10640-016-0057-8}{link} ]
\item \textbf{Aggregated versus individual land-use models: Modeling spatial
autocorrelation to increase predictive accuracy} (with Raja
Chakir and Julie Le Gallo). \emph{Environmental Modeling and
Assessment}, 2017, 22(2): 129--145. [ \href{bib/LUMP.bib}{bib} ; \href{doc/LUMP-FILE.pdf}{file} ; \href{doc/LUMP-SUP.pdf}{sup} ; \href{https://link.springer.com/article/10.1007/s10666-016-9523-5}{link} ;
\href{https://github.com/jsay/spatial-pred-R}{online} ]
\item \textbf{The economics of land use reveals a selection bias in tree
species distribution models} (with Joannès Guillemot, Nicolas
Martin-St Paul, Luc Doyen, and Paul Leadley). \emph{Global Ecology and
Biogeography}, 2017, 26(1):65--77. [ \href{bib/NTSDM.bib}{bib} ; \href{doc/NTSDM-FILE.pdf}{file} ; \href{doc/NTSDM-PRES.pdf}{pres} ; \href{doc/NTSDM-SUP.pdf}{sup} ;
\href{https://onlinelibrary.wiley.com/doi/abs/10.1111/geb.12514}{link} ]
\item \textbf{The informational content of land price and its relevance for
environmental issues} (with Laure Latruffe). \emph{Review of
Environmental and Resource Economics}, 2016, 10(3-4):183--226. [
\href{bib/RLP.bib}{bib} ; \href{doc/RLP-FILE.pdf}{file} ; \href{https://www.nowpublishers.com/article/Details/IRERE-0086}{link} ]
\item \textbf{Integrated models, scenarios and dynamics of climate, land use
and common birds} (with Raja Chakir, Luc Doyen, Frédéric Jiguet
and Paul Leadley). \emph{Climatic Change}, 2014, 126(1-2):13--30. [
\href{bib/CILE.bib}{bib} ; \href{doc/CILE-FILE.pdf}{file} ; \href{doc/CILE-SUP.pdf}{sup} ; \href{https://link.springer.com/article/10.1007/s10584-014-1202-4}{link} ; \href{https://mobilis-a4ac2.firebaseapp.com/index.html}{online}]
\item \textbf{Efficiency and equity of land conservation schemes: The effect
of policy scale} (with Claude Napoléone). \emph{Journal of
Environmental Management}, 2014, 129:190--198. [ \href{bib/EELC.bib}{bib} ; \href{http://www.sciencedirect.com/science/article/pii/S0301479713004829}{link} ]
\item \textbf{A spatial hedonic approach on land use change anticipations}
(with Ghislain Geniaux and Claude Napoléone). \emph{Journal of
Regional Science}, 2012, 51(5):967--986. [ \href{bib/SPHED.bib}{bib} ; \href{http://onlinelibrary.wiley.com/doi/10.1111/j.1467-9787.2011.00721.x/abstract}{link} ]
\end{itemize}

\soustitre{Refereed papers (in French)}
\label{sec:org8942af9}

\begin{itemize}
\item \textbf{Délivrer des permis de construire pour diminuer le coût du
foncier? Une estimation par la demande de terre constructible}
(avec Jean Cavailhès, Mohamed Hilal et Julie Le Gallo).
\emph{Économie et Statistiques}, 2018, 500-501-502, 45--67. [ \href{doc/PCPXf-FILE.pdf}{file} ;
\href{doc/PCPX-SUP.pdf}{sup} ; \href{https://insee.fr/fr/statistiques/3621977?sommaire=3622116}{link} ; \href{doc/PCPXf-PRES.pdf}{pres} ]
\item \textbf{Information sur l'hétérogénéité de la terre et délégation de la
régulation foncière.} \emph{Revue d'Économie Politique}, 2015,
125(3):453--474. [ \href{bib/IFHT.bib}{bib} ; \href{https://www.cairn.info/revue-d-economie-politique-2015-3-page-453.htm}{link} ]
\item \textbf{La gestion publique des ressources foncières: Entre évaluation
de la rareté et choix d'usage} (avec Claude Napoléone). \emph{Revue
des Régions Arides}, 2013, 30(1):177--190. [ \href{bib/GPRF.bib}{bib} ; \href{https://www.researchgate.net/profile/Claude\_Napoleone/publication/268075060\_La\_gestion\_publique\_des\_ressources\_foncieres\_entre\_evaluation\_de\_la\_rarete\_et\_choix\_d'usages/links/5460bdd20cf295b5616376de/La-gestion-publique-des-ressources-foncieres-entre-evaluation-de-la-rarete-et-choix-dusages.pdf}{file} ]
\end{itemize}

\soustitre{Working papers}
\label{sec:org2fa4729}


\begin{itemize}
\item \textbf{A bio-economic analysis for land-uses and biodiversity in
metropolitan France} (with Lauriane Mouysset, Claire Rais Assa,
Frédéric Jiguet, Romain Lorrilière and Luc Doyen). \emph{Cahiers du
GREThA 2017-05}, 2017 [ \href{http://cahiersdugretha.u-bordeaux4.fr/2017/2017-05.pdf}{link} ]
\item \textbf{Improving the estimates of agricultural land valuation: report
to the World Bank} (with Philippe Bontems, Raja Chakir and Laure
Latruffe). \emph{HAL-01462707}, 2015 [ \href{https://hal.archives-ouvertes.fr/hal-01462707}{link} ]
\item \textbf{The effects of scale, space and time on the predictive accuracy
of land use models} (with Raja Chakir and Julie Le
Gallo). \emph{Cahiers de recherche 2014/02, INRA SAE2}, 2014 [ \href{https://www6.versailles-grignon.inra.fr/economie\_publique/Media/fichiers/Working-Papers/Working-Papers-2014/WP\_2014\_02}{link} ]
\item \textbf{The empirical content of the present value model: A survey of
the instrumental uses of farmland prices} (with Laure
Latruffe). \emph{Factor Markets Working Papers}, 2013 [ \href{http://www.ceps.be/book/empirical-content-present-value-model-survey-instrumental-uses-farmland-prices.html}{link} ]
\item \textbf{La valeur des attributs naturels des terres agricoles de
Côte-d'Or} (with Jean-Marc Brayer, Jean Cavailhès, Pierre Curmi,
Mohamed Hilal and Marjorie Ubertosi). \emph{INRA UMR CESAER Working
Papers 2012-1}, 2012 [ \href{http://ideas.repec.org/p/ceo/wpaper/33.html}{link} ]
\item \textbf{Informations sur le foncier agricole pour contribuer à la
gestion de l'eau}. \emph{INRA UMR CESAER Working Papers 2011-6}, 2011
[ \href{http://ideas.repec.org/p/ceo/wpaper/32.html}{link} ]
\item \textbf{Hétérogénéité de la terre et rareté économique}. \emph{PhD thesis,
INRA and Université de Bourgogne}, 2011, [ \href{http://tel.archives-ouvertes.fr/tel-00629142/en/}{link} ]
\end{itemize}

\soustitre{Current papers}
\label{sec:org5cf235e}

\begin{itemize}
\item \textbf{Hedonic valuation of geographical indications with unobserved
terroir effects}. With Julie Le Gallo.
\item \textbf{Disease dispersion as a spatial interaction: The case of
grapevine flavescence dorée}. With Estelle Gozlan.
\item \textbf{A new method to estimate price-elasticity on wine markets}. With
Julie Le Gallo.
\item \textbf{The price of wine and the value of vineyards}. With Abdoul
Diallo and Hai Vu Pham.
\item \textbf{Willingness-to-pay for the evolution of wine geographical
indications.} With Stéphan Marette, Christophe Martin and Monia
Saïdi.
\end{itemize}

\titre{Communications}
\label{sec:orgbba9ac3}

\begin{description}
\item[{2018}] \textbf{Séminaire LARESS à l'ESA} (April, Angers, France) ;
\textbf{Journées Ingé plus} (April, Dijon, France).
\item[{2017}] \textbf{Ministère de l'écologie} (March, Paris, France) ;
\textbf{Séminaire du LEF} (March, Nancy, France) ; \textbf{Vineyard Data
Quantification Society} (May, Colmar, France) ; \textbf{Spatial
Econometrics Workshop} (May, Avignon, France) ; \textbf{Société
Française d'Écologie} (October, Marseille, France) ;
\textbf{Séminaire du LAMETA} (December, Montpellier, France) ;
\textbf{Journée du département SAE2} (December, Paris, France).
\item[{2015}] \textbf{Salon International de l'Agriculture} (February, Paris,
France) ; \textbf{Wine seminar at Kedge School of Business} (May,
Bordeaux, France) ; \textbf{American Association of Wine
Economists} (May, Mendoza, Argentina) ; \textbf{Natural Resource
Modelling workshop} (June, Bordeaux, France) ; \textbf{TRUSTEE
General Meeting} (October, Malmoe, Swedish) ; \textbf{Dialogues
Interdisciplinaires}, (December, Dijon, France).
\item[{2014}] \textbf{Global Land Project Science meeting} (March, Berlin,
Germany) ; \textbf{Métaprogramme INRA ACCAF} (December, Orléans,
France).
\item[{2013}] \textbf{VII Conference of Spatial Econometrics Association}
(July, Washington, USA) ; \textbf{Internal Seminary CRESE},
(October, Besançon, France) ; \textbf{Global Change Adaptation},
(November, Clermont-Ferrand, France) ; \textbf{Journées
INRA--SFER--CIRAD} (December, Angers, France).
\item[{2012}] \textbf{Planning, Law and Property Rights} (February, Belfast,
United Kingdom) ; \textbf{Workshop Spatial Econometrics and
Statistics} (November, Avignon, France) ; \textbf{Journées
INRA--SFER--CIRAD} (December, Toulouse, France).
\item[{2010}] \textbf{Internal Seminary Ecodéveloppement} (October, Avignon,
France).
\item[{2009}] \textbf{EAAE Ph.D. Workshop} (September, Giessen, Germany) ;
\textbf{Journées d'Étude des Sols} (May, Strasbourg, France).
\item[{2008}] \textbf{Journées INRA--SFER--CIRAD} (December, Lille, France).
\end{description}

\titre{Other activities}
\label{sec:orgd6fe5a7}
\soustitre{Research programs}
\label{sec:org1d4c72f}

\begin{itemize}
\item PubPrivLands (2019-2021) funded by \emph{Région Bourgogne
Franche-Comté (ISIT-BFC)}
\item \href{https://www.plan-deperissement-vigne.fr/travaux-de-recherche/programmes-de-recherche/risca}{Risca} (2019-2021) funded by \emph{Plan National Dépérissement du
Vignoble}
\item \href{https://www.trustee-project.eu/}{Trustee} (2013-2017) funded by EU FP7, ERA-NET RURAGRI program
\item \href{http://www.fondationbiodiversite.fr/fr/documents-frb/fiches-projets/fiches-projets-modelisation-et-scenarios.html}{Mobilis} (2012-2013) funded by FRB, \emph{Fondation pour la Recherche
sur la Biodiversité}
\item \href{http://www.gessol.fr/content/integrer-la-valeur-epuratrice-de-sols-hydromorphes-dans-leur-usage-quelles-strategies-d-inte}{EcoSolHydro} (2011-2012) funded by ADEME and MEEDE, from GESSOL
program
\end{itemize}

\soustitre{Teaching experience}
\label{sec:org48d6101}

\begin{center}
\begin{tabular}{llrll}
\textbf{Course} & \textbf{Place} & \textbf{Hours} & \textbf{Formation} & \textbf{Period}\\
\hline
Econometrics & SciencesPo Dijon & 24 & Undergraduate & 2018--2019 (1 year)\\
Economics & SciencesPo Dijon & 48 & Undergraduate & 2016--2019 (3 years)\\
Econometrics & AgroParisTech & 24 & Postgraduate & 2012--2017 (5 years)\\
Econometrics & Univ. of Franche-Comté & 18 & Postgraduate & 2012--2017 (5 years)\\
Microeconometrics & Univ. of Burgundy & 14 & Undergraduate & 2010--2011 (1 year)\\
\end{tabular}
\end{center}

\soustitre{Referee reports}
\label{sec:orgd5c45c1}

\vspace{.5cm}

Acta Oeconomica (1), Ecological Economics (2), Économie et
Statistique (2), Économie Rurale (1), European Review of
Agricultural Economics (2), International Journal of Geographical
Information Science (1), International Journal of Strategic
Property Management (1), Journal of Environmental Management (3),
Plos One (1), Regional Studies (1), Review of Agricultural, Food
and Environmental Studies (1), Revue d'Economie Régionale et
Urbaine (3), Spatial Economic Analysis (2), Spatial Statistics (1),
Sustainability (1).

\vspace{.5cm}

\soustitre{Miscellaneous}
\label{sec:org5d29856}

\begin{itemize}
\item Consultant and Expert for INAO, the French National Institute of
the Signs of Quality and Origin.
\item Consultant for Inter-Rhône, the professional organization of the
wine producers and traders from Rhône Valley.
\item Member of the scientific committee of RNEST, a national network
about the management of soil quality.
\item Expert in a scientific team about "Artificialized land and
artificialization processes: determinants, impacts and levers for
action" [ \href{http://institut.inra.fr/en/Objectives/Informing-public-policy/Scientific-Expert-Reports/All-the-news/Artificialized-land-and-artificialization-processes}{website} ].
\item Member of the scientific committee of the Workshop on Spatial
Econometrics and Statistics.
\end{itemize}
\end{document}